---
title: "Final Data Science Project: Clustered Parcels"
author: "Ke Xu Zhou, Anna Swierta, Vincent Tordo, Egdar Palencia, Zarif Normatov, Hannah Ximen"

---


# 1. Business Problem

Paack (<https://paack.co/>), a last-mile delivery service provider in Europe, is currently creating the delivery journeys for their drivers by manually grouping the daily orders they receive. It is a time-consuming process, difficult to scale, and prone to errors and inefficiencies.


# 2. Business Solution Process

The time spent on manually allocating a set of locations to drivers everyday could be saved by automatically clustering locations that should be visited by the same driver. We have chosen to run several clustering methods such as k-means to group delivery locations based on their geographical distance.

# 3. Data Sample

```{r}
print("helloworld")



ProjectDataSample <- read.csv("Paack_data_extract.csv", na.strings=c(""," ","NA"), header=TRUE, stringsAsFactors = TRUE)
ProjectDataSample <- data.matrix(ProjectDataSample) 
summary(ProjectDataSample) 
str(ProjectDataSample) 
head(ProjectDataSample)




```

# 4. Data Dictionary

```{r}
print("helloworld")
```
